Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-01 paper.tex
Add todos

@@

\rev{Since the flute instability only develops nonlinearly when using anisotropic viscosity, it is difficult to distinguish the effect of the instability from that of the viscosity itself on the viscous or Ohmic heating. TODO}

>>>>

\todo{include eqns for resistive growth rates}
\todo{write discussion on implications of resistive being non-negligible}
\todo{mention somewhere that both instabilities could be present}
\todo{note that the resistive instability may not be feasible at lower eta}
\todo{in caption of figure 8 we say development is stunted by mixing, should soften this statement}
\todo{find values for all missing items in table 1}

@@

\rev{Since the flute instability only develops nonlinearly when using anisotropic viscosity, it is difficult to distinguish the effect of the instability from that of the viscosity itself on the viscous or Ohmic heating. \todo{finish this paragraph}}
